Adopting agile in the large: motivations, success factors and challenges

### 2014-04-22 journal/article.tex
Reasons to change: Delivery speed, TTM

Some cases reported that the organization had been successful in waterfall
delivery for a long time before the agile transformation.

@@

        \multicolumn{3}{l}{Communication and collaboration dificulties}  \\
         &  Communication difficulties across and within projects  & x \\
         &  Teams work in silos or isolation  & x \\

@@

Problems
xxxxxxxxxx     Overhead in process, the process is found to be ineffective
xxx            Current processes are not taken seriously (followed)
xxxxxxxxxxxx   Dysfunction in managing software development
xx             Lack of flexibility
xxxxxxxxx      Quality issues
xx             Bad visibility and feedback of projects
xxxxxxxxxxxxx  Difficulties to schedule or estimate software development, problems with deadlines
x              Lack of knowledge transfer
xx             Motivation and morale problems
xxxx           Difficulties in customer relations and communication
x              Problems meeting business needs

x  Demand for speed (TTM)

>>>>

@@

        \multicolumn{3}{l}{Communication and collaboration dificulties}  \\
         &  Problems in communication across and within projects  & x \\
         &  Teams work in silos or isolation  & x \\

@@

The most prominent reason for introducing agile methods was the demand to
deliver software more frequently. Companies saw it critical to reduce the Time
To Market (TTM) of new features.

% Some cases reported that the organization had been successful in waterfall
% delivery for a long time before the agile transformation.
